\textbf{A Serious Game for Aiding the Screening of Dyslexia in Children and Young Adults}

### 2014-06-18 acticle.tex
Add Serious Digital Games Section

>>>>

\subsection{Serious Digital Games}
Serious games are a subset of games that aim to achieve something more than just user experience and entertainment\cite{stegeserious}. They are used in many fields, including politics, health, and education, and have serious goals such as skill acquisition, or identifying users with a particular trait, skill or deficit\cite{SeriousOverview}.

\cite{SeriousOverview} identifies the differences between serious games and those designed purely for entertainment, determining that serious games are more likely to value achieving their serious goal above rich user experience and learning above fun. This creates the question:
\cquestion{What if a rich user experience is required in order to solve the serious problem}

For example, when attempting to realistically simulate an environment in order to test a skill, the user must be completely immersed in the game environment in order to perform as they would when confronted with the same situation in reality. 
In the case of the work conducted in this paper, solving the problem and the user experience are equally important. The serious goal of this work is to accurately map users to one of two groups, those with dyslexia and those without, this accuracy is only achievable if players fully engage with the process, making user experience just as important.

The decision to make user experience equally as important as achieving the serious goal creates another goal: engaging the user. When defining the word game, it was strongly emphasised that the user should enter the game willingly, and not feel like they are being tested or forced to play, however, the user will be being tested and, in some cases, will be forced to play by a parent or teacher, this creates another question:
\cquestion{How can a game be created which hides this from the user}

The answer appears to be to carefully examine the mechanics, aesthetics, story and technology of the game in order to design a game which successfully abstracts its serious nature and goals from the user.
